Static Race Detection in OS Kernels by Mining Locking Rules

### 2023-08-01 5.evaluation.tex
Fix some grammar issues

\PP{Code analysis.} \sys can scale to large code bases of OS kernels, and it in 
total analyze xxxM lines of code in xxxK source code files within xxx hours. 
The remaining xxxM lines of code in xxxK source files are not analyzed, as they 
are not enabled by the {\em allyesconfig} for the x86-64 architecture. We 
believe that \sys can also find more data races in other architectures with 
proper configuration.

\PP{Locking-rule mining.} An OS kernel has a large code base with numerous 
variables. Handling all variables when mining locking rules can introduce much 
overhead. However, we observe that a variable tend to be protected by the lock 
stored in the same data structure as the accessed variable. Based on this 
observation, our locking-rule mining method first extract a key field by 
finding whether there exists any access to it that is protected by a lock 
stored in the same data structure. This method drops xxx\% variables (xxx out 
xxx) that need to handled when mining locking rules, and thus can reduce 
overhead significantly. After extracting key fields, our locking-rule mining 
method collect all accessed to these key fields, and then deducing locking-rule 
based on statistic. In this paper, given a data structure field, we set the 
threshold of the ratio of accesses protected by a specific lock to all accesses 
to 0.6. Our alias-aware rule mining method can drop many false rules and thus 
only mines xxx rules, which can effectively reduce false data races.

\PP{Data race detection.} \sys reports 341 data races in the kernel source 
code. We spent 15 hours on checking these data races and identify that 273 of 
them are real, with a false positive rate of 19.9\%. Besides, our lock-usage 
analysis drops 63 false data races and the results shows that it can reduce 
false positives significantly.

\PP{Data race estimation.} Many data races are benign and can not cause memory 
or logic bugs, and thus developers are unwilling to put effort into repairing 
them. We exploit three patterns to detect null-pointer dereferences, data 
inconsistency and unprotected write as introduced in 
Section~\ref{subsec_estimation}, and find 88 data races in these patterns. We 
report them to developers and 32 of them have been confirmed and fixed by them. 
We still wait for response of other data races. Moreover, one of the developers 
wonders if \sys can be used in their CI to detect these problems. 
The results show that our pattern-based estimation can extract harmful data 
races effectively, and can considerably reduce the workload of developers.

@@

First, \sys employs an alias-aware rule mining method to deduce locking rules. 
To improve the precision of mined rules, it assumes that the accessed variable 
and the protecting lock are stored in the same data structure. Even so, \sys 
can also deduce some false rules because some developers does not use locks 
properly. They take a lock/unlock pair to protect accesses to all fields in the 
same data structure, instead of the exact field should be protected for 
convenience. As a result, our alias-aware rule mining method infers that 
accesses to all fields surrounded by the lock/unlock pair should be protected 
by the lock. This reason causes \sys to report 47 false data races.

@@

Figure~\ref{fig_demo_false_rule} shows a false data race caused by an incorrect 
locking rule. In this example, only accesses to {\em cmd->t\_state} and {\em 
cmd->transport\_state} should be protected by the lock {\em 
cmd->t\_state\_lock}. However, the lock operation is put ahead of the switch 
statement by developers, making our alias-aware rule mining method deduces that 
{\em cmd->scsi\_status} and {\em cmd->se\_cmd\_flags} also need to be protected 
by {\em cmd->t\_state\_lock} mistakenly. Based on this incorrect locking rule, 
\sys reports a false positive at Line 745 when {\em cmd->se\_cmd\_flags} is 
accessed in an if statement. Although this data race is a false positive, it 
can cause performance degradation because the critical zone protected by the 
lock/unlock pair should have been limited to Lines 899-900.

@@

Apart from false data races caused by the two main reasons, there are still 7 
other data races. \sys regards function without caller functions in a kernel 
module as entry function and starts analysis from these entries. However, in 4 
cases, an assertion is put at the beginning of the entry function, to guarantee 
that the required lock is held, but \sys does not consider assertions and the 
subsequent accesses are regarded as unprotected. Other 3 false data races are 
accessed with {\em READ\_ONCE} or {\em WRITE\_ONCE}, and can not cause serious 
issues.

@@

First, our alias-aware mining method only considers accessed variables and 
protecting locks that exist in the same data structure. However, on the one 
hand, some accesses to variables may be protected by a global lock in a module, 
and this lock is used to protect accesses to various variables and does 
not exist in any data structure. On the other hand, some special lock 
-acquiring/release functions (such as {\em rcu\_read\_lock} and {\em 
rcu\_read\_unlock}) does not have an argument and is not handled in an alias 
graph. Therefore, locking rules in the above two cases can be missed by our 
alias-aware mining method. As a result, data races violated these locking rules 
can not detected by \sys.

@@

Finally, \sys exploits a lock-usage analysis to filter out false data races 
caused by code paths that can not execute concurrently. Specifically, the 
lock-usage analysis extracts all functions that are reachable from the lock 
initialization functions in a call graph with the union-find set, and assumes 
that these functions can not execute concurrently. However, some functions can 
be called at multiple program sites, and some of the program sites may be not 
reachable from lock initialization functions, but data races exist in these 
functions are are all dropped by our lock-usage analysis.

>>>>

\PP{Code analysis.} \sys can scale to large code bases of OS kernels, and it in 
total analyzes xxxM lines of code in xxxK source code files within xxx hours. 
The remaining xxxM lines of code in xxxK source files are not analyzed, as they 
are not enabled by the {\em allyesconfig} for the x86-64 architecture. We 
believe that \sys can also find more data races in other architectures with 
proper configuration.

\PP{Locking-rule mining.} An OS kernel has a large code base with numerous 
variables. Handling all variables when mining locking rules can introduce much 
overhead. However, we observe that a variable tends to be protected by the lock 
stored in the same data structure as the accessed variable. Based on this 
observation, our locking-rule mining method first extracts a key field by 
finding whether there exists any access to it that is protected by a lock 
stored in the same data structure. This method drops xxx\% variables (xxx out 
xxx) that need to be handled when mining locking rules, and thus can reduce 
overhead significantly. After extracting key fields, our locking-rule mining 
method collects all accesses to these key fields, and then deduces locking-rule 
based on statistics. In this paper, given a data structure field, we set the 
threshold of the ratio of accesses protected by a specific lock to all accesses 
to 0.6. Our alias-aware rule mining method can drop many false rules and thus 
only mines xxx rules, which can effectively reduce false data races.

\PP{Data race detection.} \sys reports 341 data races in the kernel source 
code. We spent 15 hours on checking these data races and identify that 273 of 
them are real, with a false positive rate of 19.9\%. Besides, our lock-usage 
analysis drops 63 false data races and the results show that it can reduce 
false positives significantly.

\PP{Data race estimation.} Many data races are benign and can not cause memory 
or logic bugs, and thus developers are unwilling to put effort into repairing 
them. We exploit three patterns to detect null-pointer dereferences, data 
inconsistency and unprotected write as introduced in 
Section~\ref{subsec_estimation}, and find 88 data races in these patterns. We 
report them to developers and 32 of them have been confirmed and fixed by them. 
We still wait for the response of other data races. Moreover, one of the 
developers wonders if \sys can be used in their CI to detect these problems. 
The results show that our pattern-based estimation can extract harmful data 
races effectively, and can considerably reduce the workload of developers.

@@

First, \sys employs an alias-aware rule mining method to deduce locking rules. 
To improve the precision of mined rules, it assumes that the accessed variable 
and the protecting lock are stored in the same data structure. Even so, \sys 
can also deduce some false rules because some developers do not use locks 
properly. They take a lock/unlock pair to protect accesses to all fields in the 
same data structure, instead of the exact field that should be protected for 
convenience. As a result, our alias-aware rule mining method infers that 
accesses to all fields surrounded by the lock/unlock pair should be protected 
by the lock. This reason causes \sys to report 47 false data races.

@@

Figure~\ref{fig_demo_false_rule} shows a false data race caused by an incorrect 
locking rule. In this example, only accesses to {\em cmd->t\_state} and {\em 
cmd->transport\_state} should be protected by the lock {\em 
cmd->t\_state\_lock}. However, the lock operation is put ahead of the switch 
statement by developers, making our alias-aware rule mining method deduce that 
{\em cmd->scsi\_status} and {\em cmd->se\_cmd\_flags} also need to be protected 
by {\em cmd->t\_state\_lock} mistakenly. Based on this incorrect locking rule, 
\sys reports a false positive at Line 745 when {\em cmd->se\_cmd\_flags} is 
accessed in an if statement. Although this data race is a false positive, it 
can cause performance degradation because the critical zone protected by the 
lock/unlock pair should have been limited to Lines 899-900.

@@

Apart from false data races caused by the two main reasons, there are still 7 
other data races. \sys regards a function without caller functions in a kernel 
module as the entry function and starts analysis from these entries. However, 
in 4 cases, an assertion is put at the beginning of the entry function, to 
guarantee that the required lock is held, but \sys does not consider assertions 
and the subsequent accesses are regarded as unprotected. The other 3 false data 
races are accessed with {\em READ\_ONCE} or {\em WRITE\_ONCE}, and can not 
cause serious issues.

@@

First, our alias-aware mining method only considers accessed variables and 
protecting locks that exist in the same data structure. However, on the one 
hand, some accesses to variables may be protected by a global lock in a module, 
and this lock is used to protect accesses to various variables and does 
not exist in any data structure. On the other hand, some special lock 
-acquiring/release functions (such as {\em rcu\_read\_lock} and {\em 
rcu\_read\_unlock}) do not have an argument and are not handled in an alias 
graph. Therefore, locking rules in the above two cases can be missed by our 
alias-aware mining method. As a result, data races that violate these locking 
rules can not be detected by \sys.

@@

Finally, \sys exploits a lock-usage analysis to filter out false data races 
caused by code paths that can not execute concurrently. Specifically, the 
lock-usage analysis extracts all functions that are reachable from the lock 
initialization functions in a call graph with the union-find set, and assumes 
that these functions can not execute concurrently. However, some functions can 
be called at multiple program sites, and some of the program sites may be not 
reachable from the lock initialization functions, but data races that exist in 
these functions are all dropped by our lock-usage analysis.

### 2023-08-01 6.discussion.tex
Fix some grammar issues

\PP{Benefits in other aspects.} \sys uses an alias-aware mining method to 
deduce precise locking rules about whether accesses to a variable should be 
protected by a lock, and which lock are required. Such rules can benefit in 
various aspects.

First, with these rules, developers can improve reliability 
and performance of kernel code. On the one hand, developers can carefully check 
whether necessary lock are used when writing code, and avoid serious bugs 
caused by data races in the early developing stage. On the other hand, 
developers can limit the critical zone protected by an lock/unlock pair to the 
exact accesses that should be protected, and let other code can execute 
concurrently. And these locking rules can also help improve documents of OS 
kernels, which is benefit for long term evolution of kernel codes.

Second, key fields extract \sys are data structure fields that is protected by 
some locks, and this means that these fields is likely to be concurrently 
accessed by different threads. Therefore, key fields can be used in detecting 
various types of concurrency bugs such as use-after-free and 
uninitialized-variable access. Take concurrency use-after-free as an example, 
if a key field is accessed in one thread and freed in another thread, a 
concurrency use-after-free can occur.

Finally, the locking rules deduced by our alias-aware rule mining method can 
enhance other annotation-based analysis such as Clang thread safety 
analysis~\cite{ClangThreadSafety}. Specifically, developers can use 
instrumentation to annotate necessary locks for specific variables in the code 
automatically, according to the locking rules generated by \sys, and run other 
annotation-based analysis to detect data races.

\PP{Comparison to other approaches.} We have try our best to experimentally 
compare \sys to existing works in data race detection including 
RELAY~\cite{Voung:FSE07}, WHOOP~\cite{Deligiannis:ASE15} and 
Goblint~\cite{Vojdani:ASE16}. Unfortunately, they are too old and generate too 
many errors when compiling and running, and thus we compare \sys to them 
methodologically.

\PP{Limitations and future works.} \sys can be improved in some aspects. First, 
our alias-aware mining method only considers accessed variables and protecting 
locks that exist in the same data structure, and can miss some locking rules 
involves special locks such as RCU locks. To overcome this limitation, we plan 
to create a common virtual node for RCU lock in the alias graph, and regard it 
as the ancestor of all other nodes. In this way, all variables have a common 
ancestor with the RCU lock, and can be inferred to be protected by the RCU 
lock, because the accessed variable and the RCU lock are existing in the 
identical data structure by our alias-aware rule mining method. Second, \sys 
does not handle function-pointer calls, and thus it can not build complete call 
graphs, and thus can miss data races reached from function-pointer calls. To 
relieve this limitation, we plan to apply existing function-pointer 
analysis~\cite{Hind:TOPLAS99, Zhang:ISPEC15, Heintze:PLDI01} in \sys, to detect 
more data races in functions that called through function pointers and reduce 
false negatives. Third, \sys performs a path-based analysis and suffers from 
high time overhead, to accelerate its analysis, we plan to employ summer-based 
analysis~\cite{Bai:ATC19, Bai:ATC22} to avoid re-analysis of the same function 
definition. Finally, we plan to apply \sys to detect data races in other OS 
kernels such as FreeBSD~\cite{FreeBSD} and NetBSD~\cite{NetBSD}, and use it to 
detect more types of concurrency bugs including use-after-free and 
uninitialized-variable access.

>>>>

\PP{Benefits in other aspects.} \sys uses an alias-aware mining method to 
deduce precise locking rules about whether accesses to a variable should be 
protected by a lock, and which lock is required. Such rules can benefit in 
various aspects.

First, with these rules, developers can improve the reliability 
and performance of kernel code. On the one hand, developers can carefully check 
whether necessary locks are used when writing code, and avoid serious bugs 
caused by data races in the early developing stage. On the other hand, 
developers can limit the critical zone protected by a lock/unlock pair to the 
exact accesses that should be protected, and let other code can execute 
concurrently. And these locking rules can also help improve documents of OS 
kernels, which is beneficial  for long term evolution of kernel codes.

Second, key fields extracted by \sys are data structure fields that are 
protected by some locks, and this means that these fields are likely to be 
concurrently accessed by different threads. Therefore, key fields can be used 
in detecting various types of concurrency bugs such as use-after-free and 
uninitialized-variable access. Take concurrency use-after-free as an example, 
if a key field is accessed in one thread and freed in another thread, a 
concurrency use-after-free can occur.

Finally, the locking rules deduced by our alias-aware rule mining method can 
enhance other annotation-based analyses such as Clang thread safety 
analysis~\cite{ClangThreadSafety}. Specifically, developers can use 
instrumentation to annotate necessary locks for specific variables in the code 
automatically, according to the locking rules generated by \sys, and run other 
annotation-based analysis to detect data races.

\PP{Comparison to other approaches.} We have tried our best to experimentally 
compare \sys to existing works in data race detection including 
RELAY~\cite{Voung:FSE07}, WHOOP~\cite{Deligiannis:ASE15} and 
Goblint~\cite{Vojdani:ASE16}. Unfortunately, they are too old and generate too 
many errors when compiling and running, and thus we compare \sys to them 
methodologically.

\PP{Limitations and future works.} \sys can be improved in some aspects. First, 
our alias-aware mining method only considers accessed variables and protecting 
locks that exist in the same data structure, and can miss some locking rules 
involving special locks such as RCU locks. To overcome this limitation, we plan 
to create a common virtual node for RCU lock in the alias graph, and regard it 
as the ancestor of all other nodes. In this way, all variables have a common 
ancestor with the RCU lock, and can be inferred to be protected by the RCU 
lock, because the accessed variable and the RCU lock are existing in the 
identical data structure by our alias-aware rule mining method. Second, \sys 
does not handle function-pointer calls, and thus it can not build complete call 
graphs, and thus can miss data races reached from function-pointer calls. To 
relieve this limitation, we plan to apply existing function-pointer 
analysis~\cite{Hind:TOPLAS99, Zhang:ISPEC15, Heintze:PLDI01} in \sys, to detect 
more data races in functions that are called through function pointers and 
reduce false negatives. Third, \sys performs a path-based analysis and suffers 
from high time overhead, to accelerate its analysis, we plan to employ 
summer-based analysis~\cite{Bai:ATC19, Bai:ATC22} to avoid re-analysis of the 
same function definition. Finally, we plan to apply \sys to detect data races 
in other OS kernels such as FreeBSD~\cite{FreeBSD} and NetBSD~\cite{NetBSD}, 
and use it to detect more types of concurrency bugs including use-after-free 
and uninitialized-variable access.

### 2023-08-01 7.related.tex
Fix some grammar issues

\subsection{Static Analysis of Data Races}
\label{subsec_static}
Many approaches~\cite{Boyapati:OOPSLA02, Anderson:PLDI08, Anderson:PLDI09, 
Zhou:MICRO19, Flanagan:PASTE01, Flanagan:PLDI00, Sadowski:PLATEAU14, 
ClangThreadSafety, Blackshear:OOPSLA18, Choi:PLDI02, Engler:SOSP03, 
Voung:FSE07, Pratikakis:PLDI06, Naik:PLDI06} use static analysis to detect data 
races, without running the checked program. Some of 
them~\cite{Boyapati:OOPSLA02, Anderson:PLDI08, Anderson:PLDI09, Zhou:MICRO19, 
Flanagan:PASTE01, Flanagan:PLDI00, Sadowski:PLATEAU14, ClangThreadSafety} 
perform annotation-based analysis, and request developers to provide locking 
rules about which lock is required when a specific variable is accessed, and 
then detect data races that violate the provided rules. Clang thread safety 
analysis~\cite{ClangThreadSafety} needs developers to annotate code with a {\tt 
GUARDED\_BY} attribute to indicate which lock is required for a specific 
variable, and then works like a type system for multi-threaded 
programs~\cite{Vu:SoICT12, Boyapati:OOPSLA02, Marion:TAMC14} to detect data 
races that violate the provided attribute. Flanagan et 
al.~\cite{Flanagan:PLDI00} design a type system and relay on developers to 
provide additional type annotations to associate a protecting lock with each 
field declaration, and tracks the set of locks held at each program point. And 
then it identifies whether a given program is race free by checking whether 
necessary locks are indeed held at each program site. However, such 
annotation-based approaches are not suitable for race detection in OS kernels, 
because even an expert developer can not provide accurate annotations, because 
the locking rules of kernel code are not well documented, and the logic of 
kernel code tends to be very complex. Other 
approaches~\cite{Blackshear:OOPSLA18, Choi:PLDI02, Engler:SOSP03, Voung:FSE07, 
Pratikakis:PLDI06, Naik:PLDI06} employ lockset-based analysis to detect data 
races automatically. They deduce locking rules based on statistic instead of 
relying on manual annotations. But they does not consider alias 
relationships~\cite{Voung:FSE07, Engler:SOSP03} or just employ imprecise 
flow-insensitive alias analysis~\cite{Choi:PLDI02, 	Pratikakis:PLDI06, 
Naik:PLDI06}. RacerX~\cite{Engler:SOSP03} performs a lockset 
analysis to to detect data races in three modes, including simple checking, 
simple statistical and precise statistical from least to most precise. However, 
even if for the most precise mode, RacerX does not employ any alias analysis, 
and thus introduce many false positives and negatives.

Different from the above static analysis, \sys employs the alias graph to mine 
locking rules automatically. Benefit from the path-based and field-sensitive 
alias relationships generated by alias graph, \sys can deduce locking rules 
effectively. With these locking rules, \sys can detect data races accurately. 
Moreover, \sys exploits a pattern-based estimation to extract harmful data 
races automatically, and can help developers focus on data races that can 
indeed introduce serious issues.

\subsection{Dynamic Analysis of Data Races}
\label{subsec_dynamic}
Runtime analysis does not suffer from the pointer alias problems, and thus many 
approaches~\cite{Lochmann:EuroSys19, Lu:SOSP07, Lu:FSE18, Joshi:ASE08, 	
Liu:NSDI07, Ocallahan:PPoPP03, Serebryany:WBIA09, Marino:PLDI09} detect data 
races through dynamic analysis. LockDoc~\cite{Lochmann:EuroSys19} records 
accesses to variables and lock acquisitions of an instrumented Linux kernel in 
logs, and then infers locking rules from the logs. After that, LockDoc 
automatically detect data races by checking whether a given variable access 
violates the inferred locking rules. O'callahan et al.~\cite{Ocallahan:PPoPP03} 
combine lockset-based detection and happens-before-based detection to detect 
data races, which can get fewer false positives and less overhead than previous 
dynamic analysis. In order to reduce overhead of runtime overhead further, 
LiteRace~\cite{Marino:PLDI09} employs a sampling-based approach based on the 
hypothesis that data races are likely to occur when a thread is executing
an infrequently accessed region in the program. It instruments sampled memory 
accesses, and perform happens-before-based analysis to detect data races, 
according the logs generated by the instrumentation.

>>>>

\subsection{Static Analysis of Data Races}
\label{subsec_static}
Many approaches~\cite{Boyapati:OOPSLA02, Anderson:PLDI08, Anderson:PLDI09, 
Zhou:MICRO19, Flanagan:PASTE01, Flanagan:PLDI00, Sadowski:PLATEAU14, 
ClangThreadSafety, Blackshear:OOPSLA18, Choi:PLDI02, Engler:SOSP03, 
Voung:FSE07, Pratikakis:PLDI06, Naik:PLDI06} use static analysis to detect data 
races, without running the checked program. Some of 
them~\cite{Boyapati:OOPSLA02, Anderson:PLDI08, Anderson:PLDI09, Zhou:MICRO19, 
Flanagan:PASTE01, Flanagan:PLDI00, Sadowski:PLATEAU14, ClangThreadSafety} 
perform annotation-based analysis, and request developers to provide locking 
rules about which lock is required when a specific variable is accessed, and 
then detect data races that violate the provided rules. Clang thread safety 
analysis~\cite{ClangThreadSafety} needs developers to annotate code with a {\tt 
GUARDED\_BY} attribute to indicate which lock is required for a specific 
variable, and then works like a type system for multi-threaded 
programs~\cite{Vu:SoICT12, Boyapati:OOPSLA02, Marion:TAMC14} to detect data 
races that violate the provided attribute. Flanagan et 
al.~\cite{Flanagan:PLDI00} design a type system and rely on developers to 
provide additional type annotations to associate a protecting lock with each 
field declaration, and track the set of locks held at each program point. And 
then it identifies whether a given program is race free by checking whether 
necessary locks are indeed held at each program site. However, such 
annotation-based approaches are not suitable for race detection in OS kernels, 
because even an expert developer can not provide accurate annotations, because 
the locking rules of kernel code are not well documented, and the logic of 
kernel code tends to be very complex. Other 
approaches~\cite{Blackshear:OOPSLA18, Choi:PLDI02, Engler:SOSP03, Voung:FSE07, 
Pratikakis:PLDI06, Naik:PLDI06} employ lockset-based analysis to detect data 
races automatically. They deduce locking rules based on statistics instead of 
relying on manual annotations. But they do not consider alias 
relationships~\cite{Voung:FSE07, Engler:SOSP03} or just employ imprecise 
flow-insensitive alias analysis~\cite{Choi:PLDI02, 	Pratikakis:PLDI06, 
Naik:PLDI06}. RacerX~\cite{Engler:SOSP03} performs a lockset analysis to detect 
data races in three modes, including simple checking, simple statistical and 
precise statistical from least to most precise. However, even if for the most 
precise mode, RacerX does not employ any alias analysis, and thus introduces 
many false positives and negatives.

Different from the above static analysis, \sys employs the alias graph to mine 
locking rules automatically. Benefiting from the path-based and field-sensitive 
alias relationships generated by alias graphs, \sys can deduce locking rules 
effectively. With these locking rules, \sys can detect data races accurately. 
Moreover, \sys exploits a pattern-based estimation to extract harmful data 
races automatically, and can help developers focus on data races that can 
indeed introduce serious issues.

\subsection{Dynamic Analysis of Data Races}
\label{subsec_dynamic}
The runtime analysis does not suffer from the pointer alias problems, and thus 
many approaches~\cite{Lochmann:EuroSys19, Lu:SOSP07, Lu:FSE18, Joshi:ASE08, 	
Liu:NSDI07, Ocallahan:PPoPP03, Serebryany:WBIA09, Marino:PLDI09} detects data 
races through dynamic analysis. LockDoc~\cite{Lochmann:EuroSys19} records 
accesses to variables and lock acquisitions of an instrumented Linux kernel in 
logs, and then infers locking rules from the logs. After that, LockDoc 
automatically detect data races by checking whether a given variable access 
violates the inferred locking rules. O'callahan et al.~\cite{Ocallahan:PPoPP03} 
combine lockset-based detection and happens-before-based detection to detect 
data races, which can get fewer false positives and less overhead than previous 
dynamic analyses. In order to reduce runtime overhead further, 
LiteRace~\cite{Marino:PLDI09} employs a sampling-based approach based on the 
hypothesis that data races are likely to occur when a thread is executing
an infrequently accessed region in the program. It instruments sampled memory 
accesses, and performs happens-before-based analysis to detect data races, 
according to the logs generated by the instrumentation.
